### 2022-08-25 main/chapter_searches.tex
dump a bunch of notes from reading

\TODO{
Fisher:
criteria for estimators,
(consistency, efficiency, sufficiency)
https://royalsocietypublishing.org/doi/pdf/10.1098/rsta.1922.0009
testing, p-value,
likelihood, also ratios of p-values (here named probable errors)
https://digital.library.adelaide.edu.au/dspace/handle/2440/15169
tail area = significance
http://psychclassics.yorku.ca/Fisher/Methods/
}

\TODO{
Fisher:
``We can know nothing of the probability of hypotheses or of hypothetical
quantities.''
}

>>>>

\TODO{
Fisher:
criteria for estimators,
(consistency, efficiency, sufficiency)
https://royalsocietypublishing.org/doi/pdf/10.1098/rsta.1922.0009
testing, p-value,
likelihood, also ratios of p-values (here named probable errors)
(introduced the term likelihood? cite?)
https://digital.library.adelaide.edu.au/dspace/handle/2440/15169
tail area = significance
http://psychclassics.yorku.ca/Fisher/Methods/
}

\TODO{
Fisher:
``We can know nothing of the probability of hypotheses or of hypothetical
quantities.''
Fisher:
``absurdly academic''
Fisher:
``There is something horrifying in the ideological movement represented by the doctrine
that reasoning, properly speaking, cannot be applied to empirical data to lead to inferences
valid in the real world.''
}

\TODO{
Nayman-Pearson:
Seek good test statistics --
likelihood ratio intuitive for two-hypothesis comparison
prove it optimal in a reasonable sense
idea of long-run mostly not wrong
recede to maximum likelihood ratios
https://www.jstor.org/stable/2331945
``for which hypothesis A is more probable and those for which it is less
probable (sic!)''
unbiased (unbiassed) test differs from unbiasedness of estimator
``Then the two corresponding densities at the sample point
are (Al) 6-42 x 10-20, (A2) 5 18*x 1O-4 and the ratio of the likelihood of Hypothesis
Al to- that of A2 is 1P24 x 10-16. This ratio confirms the common-sense judgment
that A2 is far more plausible than A1''
^ Another posterior argument --- this likelihood ratio in in fact a change
in plausibilities. For example, if A2 is an inconsistent, self-contradictory
theory, it is totally implausible, and not more plausible despite predicting
these data better.
``The statistician can
balance the numerical verdict of likelihood against the vaguer expectations de-
rived from 'a priori considerations, and it must be left to his judgment to
at what point the evidence in favour of alternative hypotheses becomes so con-
vincing that Hypothesis A must be rejected.''
Introduce maximum likelihood ratio as interesting without claiming it to be
necessarily best.
https://royalsocietypublishing.org/doi/10.1098/rsta.1933.0009
Neyman-Pearson lemma
https://www.cambridge.org/core/journals/canadian-mathematical-bulletin/article/a-selection-of-early-statistical-papers-of-j-neyman-university-of-california-press-1967-ix-429-pages-1495/75CE96368E6F34BD25D06BAF6DC8E69F
}

\TODO{
discrete failure to match --- randomization
K. D. Tocher (1950)
``extraneous randomization''
}

\TODO{
Given all this understanding, what I do not understand is their choice to
convert this to a $p$-value.
Seems to be this idea of long-run correctness guarantees.
But their derivation does rely on long-run frequencies.
}
